The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
comment out confusing

In contrast to spatial networks, where nodes represent spatial locations that
are fixed in space, movement networks can represent continuous and simultaneous
movement trajectories of multiple animals. In a recent study of vulturine
gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate
monolayer association networks within a multilayer network [@Papageorgiou_2019].
However, despite potential to generate networks in different spatial or social
contexts, layers in the multilayer network represented social associations
within and between groups. Continuous collection of animal relocation data using
GPS technology can be used to measure how groups of animals make collective
movement decisions in the context of their local environment
[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
collective movement layer could constitute similarity in movement for dyads
[@Long_2014] or groups [@Bode_2011]. This movement layer could be made at a
fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
@Flack_2018]. Our case study integrates variation in temporal and spatial scale
to assess the role of scale in predicting multilayer networks. As one might
expect, we found increasing social threshold results in saturation of potential
social connections (Figure \@ref(fig:socres)), while increasing temporal scale had little effect
<!-- TODO:.........-->
on habitat-specific networks (Figure \@ref(fig:)). Another potential application would be
to generate social networks during times when animals are engaged in different
behaviours, including traveling, interacting, or foraging [@Muller_2018;
@Finn_2019] and construct a multilayer network based on behaviour-specific
monolayer networks [e.g. @Smith_Aguilar_2019].

>>>>

In contrast to spatial networks, where nodes represent spatial locations that
are fixed in space, movement networks can represent continuous and simultaneous
movement trajectories of multiple animals. In a recent study of vulturine
gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate
monolayer association networks within a multilayer network [@Papageorgiou_2019].
However, despite potential to generate networks in different spatial or social
contexts, layers in the multilayer network represented social associations
within and between groups. Continuous collection of animal relocation data using
GPS technology can be used to measure how groups of animals make collective
movement decisions in the context of their local environment
[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
collective movement layer could constitute similarity in movement for dyads
[@Long_2014] or groups [@Bode_2011]. This movement layer could be made at a
fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
@Flack_2018]. Our case study integrates variation in temporal and spatial scale
to assess the role of scale in predicting multilayer networks. As one might
expect, we found increasing social threshold results in saturation of potential
social connections (Figure \@ref(fig:socres)).<!--TODO: what??, while increasing temporal scale had little effect
on habitat-specific networks (Figure \@ref(fig:))-->. Another potential application would be
to generate social networks during times when animals are engaged in different
behaviours, including traveling, interacting, or foraging [@Muller_2018;
@Finn_2019] and construct a multilayer network based on behaviour-specific
monolayer networks [e.g. @Smith_Aguilar_2019].
